14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-16 rules/rules19.tex
Rules: Reorder
Benchmark selection section updated

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
	and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2019.
The principal changes from the previous competition rules are the following: \todo{Aina in charge of this section}
\begin{itemize}
  \item {\it Renaming of Tracks.} This year, the track previously known as
    `Main Track` will be renamed to \emph{\maintrack}, and the previous
    `Application Track' will be renamed to \emph{\inctrack}.
    \emph{Rationale:} We believe the current names are misleading, as the
    previous `Main Track' also contains problems coming from applications.
    Additionally, having it called `Main' de-emphasizes the importance of the
    other tracks and use cases of SMT.

  \item {\it Mandatory System Descriptions.}
    SMT-COMP entrants are now required to provide a short (1–2 pages)
    description of the system.  \emph{Rationale:} The main incentive for this
    change is twofold.  First, we want to improve transparency when submitted
    solvers are wrapper tools according to the rules of the competition.
    Second, we want to encourage documentation of technical improvements that
    lead to the current results.

@@

  \item {\it Time Limit.} The time limit per solver/benchmark pair is
    anticipated to be at most 40 minutes in the \maintrack (previously: Main Track),
    \inctrack, \ucoretrack and \mvaltrack.  For the
    \challtrack, it is anticipated to be at most 720 (12 hours) minutes.
    \emph{Rationale:} In 2017 and 2018, the time limit for the Main Track was
    reduced to 20 minutes (down from 40 minutes in earlier years) to cope with
    the inclusion of a large number of benchmarks with unknown status.  This
    year, the reduced number of benchmarks selected per division allows us to
    increase the time limit back to 40 minutes for the \maintrack.  For the
    \challtrack, 12 hours seem to be a reasonable compromise for the
    expected number of participants and benchmarks submitted to this track.

  \item {\it New \challtrack.} \todo{}
.
  \item {\it New Scores.} \todo{24 seconds, sat, unsat}

@@

\header{Benchmark selection.} \todo{Antti covers this section}
%
The competition will use a large subset of SMT-LIB benchmarks.  The
benchmark pool is culled as follows:
\todo{add information about how benchmarks are selected for the \mvaltrack,
\challtrack, \ucoretrack, and the 24s, sat and unsat scores}
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \todo{\emph{Remove benchmarks solved by all solvers within 1s in the previous year}}
\end{enumerate}
%
\todo{update with the new benchmark selection rules}
All remaining benchmarks are used for the competition.  There will be
no further selection of benchmarks, e.g., based on benchmark
difficulty or benchmark category.

The set of benchmarks selected for the competition will be published
when the competition begins.

\todo{add information about how benchmarks are selected for the \mvaltrack,
\challtrack, \ucoretrack, and the 24s, sat and unsat scores -- either here
or below}

\todo{For Unsatcore remove all benchmarks with a single assertion, otherwise use same procedure as last year... check what that was}

>>>>

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
	and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2019.
The principal changes from the previous competition rules are the following: \todo{Aina in charge of this section}
\begin{itemize}
  \item {\it Mandatory System Descriptions.}
    SMT-COMP entrants are now required to provide a short (1–2 pages)
    description of the system.  \emph{Rationale:} The main incentive for this
    change is twofold.  First, we want to improve transparency when submitted
    solvers are wrapper tools according to the rules of the competition.
    Second, we want to encourage documentation of technical improvements that
    lead to the current results.

  \item {\it Renaming of Tracks.} This year, the track previously known as
    `Main Track` will be renamed to \emph{\maintrack}, and the previous
    `Application Track' will be renamed to \emph{\inctrack}.
    \emph{Rationale:} We believe the current names are misleading, as the
    previous `Main Track' also contains problems coming from applications.
    Additionally, having it called `Main' de-emphasizes the importance of the
    other tracks and use cases of SMT.

  \item {\it New \challtrack.} \todo{}
.
  \item {\it Time Limit.} The time limit per solver/benchmark pair is
    anticipated to be at most 40 minutes in the \maintrack (previously: Main Track),
    \inctrack, \ucoretrack and \mvaltrack.  For the
    \challtrack, it is anticipated to be at most 720 (12 hours) minutes.
    \emph{Rationale:} In 2017 and 2018, the time limit for the Main Track was
    reduced to 20 minutes (down from 40 minutes in earlier years) to cope with
    the inclusion of a large number of benchmarks with unknown status.  This
    year, the reduced number of benchmarks selected per division allows us to
    increase the time limit back to 40 minutes for the \maintrack.  For the
    \challtrack, 12 hours seem to be a reasonable compromise for the
    expected number of participants and benchmarks submitted to this track.

  \item {\it New Scores in the \maintrack.} \todo{24 seconds, sat, unsat}

@@

@@

\header{Benchmark selection.} \todo{Antti covers this section}
%
The competition will use a large subset of SMT-LIB benchmarks.  In all
tracks the following process will be used for culling the benchmark
pool.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy benchmarks.} The competition organizers will
  remove all benchmarks that were solved by all solvers (including the
  non-competitive solvers) in the 2018 SMT competition.
\item \emph{Cap the number of instances in a division.} The competition
  organizers will limit the number of benchmarks in a division as
  follows:
  \begin{enumerate}
  \item If a division contains less than 300 instances, all
        the instances will selected.
  \item If a division contains between 300 and 600 instances, a
        random selection of 300 instances from the set will be used.
  \item If a division contains more than 600 instances, 50\% of
        the benchmarks will be randomly selected.
  \end{enumerate}
\item \emph{\ucoretrack{}.} In addition, for the \ucoretrack{}, all
  benchmarks with a single assertion will be removed.
\end{enumerate}
%
The culling script will be publicly available and use the same random
seed as the rest of the competition, and the set of benchmarks selected
for the competition will be published when the competition begins.
